Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/appendix.tex
proofs of Lemmas 1 and 2

For the following proofs, recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph. Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to D\times L$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
\begin{equation}\label{eq:ideresult}
  \resultIDE(Q)=\lambda n\,.\,\lambda d\,.\,\mvp{\textsf{Env}}(n,\,d))\,.
\end{equation}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normeq}}]
    Let $\updfun f^*=\setpair I U$.
    For any $\tau\in T,$
    \[
        \begin{aligned}
            \denote{\mathcal N(\updfun f^*)}(\tau)
            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
            &=\denote{\setpair{I\cup U}U}(\tau)\\
            &=\tau\cap(I\cup U)\cup U\\
            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
            &=\tau\cap I\cup U\\
            &=\denote{\setpair IU}(\tau)\\
            &=\denote{\updfun f^*}(\tau)\,.
        \end{aligned}
    \]
    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:normuneq}}]
    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
    \begin{enumerate}
        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
            \]
            whereas 
            \[ 
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
            \]
            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
        \item $I\ne I'$. Then for the set of all types $\tau=T$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
            \]
            Since $\setpair IU$ is normalized, $U\subseteq I$, and
            \[
                I\cup U= I\,.
            \]
            At the same time,
            \[
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
            \]
            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
    \end{enumerate}
\end{proof}

>>>>

For the following proofs, recall from Section~\ref{sec:ideToIfds} that the result of an IDE analysis maps a lattice element to each node in the exploded supergraph. Specifically, for an IDE problem $Q$, the result $\resultIDE(Q):\ N^*\to(D\to L)$ maps nodes of the supergraph to pairs of data-flow facts and lattice elements~\cite{sagiv1996precise}:
\begin{equation}\label{eq:ideresult}
  \resultIDE(Q)=\lambda n\,.\,\lambda d\,.\,\mvp{\textsf{Env}}(n,\,d))\,.
\end{equation}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
\begin{align*}
  \denote{\setpair IU}(m)(r)
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
  &=(m(r)\cap I(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup U'(r)\\
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
  &=\denote{\setpair{I'}{U'}}(m)(r).
\end{align*}

For the other direction, we need to show that if for any $r\in R$ and ${m\in R\to2^T}$, $(m(r)\cap I(r))\cup U(r)=(m(r)\cap I'(r))\cup U'(r)$, then for all $r'\in R$, $I(r')=I'(r')$ and $U(r')=U'(r')$.

To prove that $U(r')=U'(r')$, we will pick $m(r)=\varnothing$.
Then by our assumption, for all $r$, $U(r)=U'(r)$, and hence $U(r')=U'(r')$.

To prove that $I(r')=I'(r')$, let us pick $m=I$. Then the assumption
is $I(r)\cup U(r)=(I(r)\cap I'(r))\cup U'(r)$. By our definition, $U(r)\subseteq I(r)$, and we just proved that $U(r')=U'(r)$. Theorefore, $I(r)=(I(r)\cap I'(r))\cup U'(r)$.
Additionally, $U'(r)\subseteq I'(r)$ and $U'(r)\subseteq I(r)$ (because $U'(r)=U(r)\subseteq I(r)$). This means that $U'(r)\subseteq I(r)\cap I'(r)$. Therefore, $I(r)=I(r)\cap I'(r)$,
and we can conclude that $I(r)=I'(r)$.
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalMeet}}]
\end{proof}

### 2014-12-15 content/impl.tex
proofs of Lemmas 1 and 2

\otodo{we agreed to move this figure to the initial example section}
  \mtodo{Move Figure~\ref{fig:cc_edgefn_example} up to where it's mentioned first? If yes, the caption won't make sense.}

@@

The implementation of function application follows directly from the definition of
the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.

To compare two micro-functions for equality, it suffices to compare the corresponding
sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
implementation of comparison corresponds to equality of the represented micro-functions:
\begin{lemma}\label{lem:equal}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}
    \] 
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

\otodo{The normalization function $\mathcal N$ was only needed in composition. I therefore
    ``inlined'' it into composition to save space. This makes composition a bit harder to intuitively
    verify, but saves complexity here. The verification can be in the proof in the supplementary appendix.}
The composition of two micro-function representations is defined as follows:
$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}$.
The following lemma shows that this implementation corresponds to the composition
of the denoted functions:
\begin{lemma}\label{lem:equal}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}
    \]
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{lemma}\label{lem:equal}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
    \]
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

>>>>

\otodo{we agreed to move this figure to the initial example section}

@@

The implementation of function application follows directly from the definition of
the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.\mtodo{Should this be the denotation of $\setpair IU$?}

To compare two micro-functions for equality, it suffices to compare the corresponding
sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
implementation of comparison corresponds to equality of the represented micro-functions:
\begin{lemma}\label{lem:equalEq}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
    \] 
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

\otodo{The normalization function $\mathcal N$ was only needed in composition. I therefore
    ``inlined'' it into composition to save space. This makes composition a bit harder to intuitively
    verify, but saves complexity here. The verification can be in the proof in the supplementary appendix.}
The composition of two micro-function representations is defined as follows:
$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}$.
The following lemma shows that this implementation corresponds to the composition
of the denoted functions:
\begin{lemma}\label{lem:equalComp}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}}.
    \]
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{lemma}\label{lem:equalMeet}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.
    \]
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
